Millions of Type Errors

### 2023-09-13 programming23/paper.tex
more abstract

  \paragraph{Inquiry}
  %% What problem or question does the paper
  %% address? How has this problem or question been
  %% addressed by others (if at all)?
  Since Luau is in the hands of so many creators,
  how do they use it?
  Of central importance, however, is protecting the privacy
  of Luau creators.
  FILL

%  TYPE ERRORS
%  investigate

  It has the ability to report telemetry data,
  which allows large-scale measurement of the creator experience. In
  this paper, we discuss one use of telemetry, to measure the experience
  of type error reporting.
  We find FILL.

  \paragraph{Approach}
  %% What was done that unveiled new knowledge?
  FILL impersonal telemetry, N months.

@@

  \paragraph{Grounding}
  %% What argument, feasibility proof, artifacts,
  %% or results and evaluation support this work?
  Our findings are supported by a publicly-available dataset
  of over 1.5 million telemetry records.

>>>>

  \paragraph{Inquiry}
  %% What problem or question does the paper
  %% address? How has this problem or question been
  %% addressed by others (if at all)?
  Our main goal is to collect feedback from creators to improve the design of
  Luau.
  We want to do so at a large scale, as creators work on their actual projects,
  which suggests we deploy client-side telemetry to report on notable events.
  However, we must respect creators privacy.
  Finding ways to harness data from telemetery without exposing any
  personally-identifiable information (such as source code) is the
  central research challenge.

  \paragraph{Approach}
  %% What was done that unveiled new knowledge?
  We designed and implemented a privacy-preserving telemetry system for Luau.
  We deployed it for approximately four months in Spring 2023, during which
  time we collected over one million telemetry records.
  The telemetry focuses on the type errors that creators encountered.

@@

  \paragraph{Grounding}
  %% What argument, feasibility proof, artifacts,
  %% or results and evaluation support this work?
  Our findings are supported by a publicly-available dataset
  of over 1.5 million telemetry records.
  We also release the code used to analyze the data.
